Fluid structure interaction with ETVF

### 2021-12-14 manuscript/paper.tex
Update examples to FSI WCSPH code.
Automate snapshot code. Wedge entry automation.

Some FSI introduction. Its importance in different fields. Its applications so
far.

In modelling FSI problems, there are mainly two ways to handle the fluid and
structures modelling. One way is to model the fluid part with mesh based
scheme and solids part also with mesh based scheme. Like how (cite many papers
which have done this). Or fluid part is modelled with a particle based scheme
and the structures part with a mesh based scheme (Cite articles which have
done this). One more way is to model both the phases using particle based
schemes. In this paper we use particle based method to model both the phases.

Recently there has been very good work on modelling fsi with particle based
methods. Specific to particle based modelling, the fluid is modelled with SPH,
and structure is modelled with different numerical method. Few articles which
have done in this regard are as follows, citet{hosseini2009particle} has
modelled the structure part using EBG method, then \citet{wu2016coupled}
modelled it with DEM, \citet{ng2020coupled} modeled it using volume
compensated particle method (VCPM), \citet{peng2021coupling} modeled it with
RKPM, citet{zhang2021deltasph} modeled it with Smoothed Point Interpolation
Method (SPIM).

Recently there have been heavy improvements to basic SPH methodology in
modelling fluid problems. Schemes such as $\delta$ SPH, $\delta +$ SPH, TVF
for internal flows and GTVF for external flows is been proposed. Also, many
new strategies were proposed to in overcoming the particle homogeneity
problem, such as IPST, which is applied in \cite{IPST paper}. Also these
improvements take care of tensile instability problem too. Another variant of
SPH is ISPH, todoin{please cite some ISPH papers here}.

Using only SPH, articles have been proposed where we model both the phases
only using SPH. To note some, \citet{He2017coupled} has modelled the fluid
part with WCSPH, \citet{Sun2019study} with delta sph,
\citet{zhan2019stabilized} with WCSPH but applied to 3d problems with GPU. All
these schemes use TLSPH as to model the structure part. And papers by Abbas use
usual Gray equations to model the structures part.

\citet{sun2019fully} couples MPS and BPM model to simulate FSI. He models both
elastic dam break and flow over an elastic obstacle.

Recently {cite our paper ETVF} has been proposed as an another extension to
TVF to model both fluid and structures part. In the current work we couple
purely Eulerian SPH based schemes to model the FSI problems. We take advantage
of the accuracy of the ETVF scheme proposed in modelling the fluids. ETVF
scheme deals with tensile instability in both fluid and solid inherently.

@@

\subsection{Solid mechanics equations}

The discretized equations of the fluid medium are

$\Pi_{ab}$ is the artificial
viscosity~\cite{monaghan-review:2005} to maintain the stability of the
numerical scheme. It is given as,
\begin{align}
  \label{eq:mom-av}
  \Pi_{ab} =
  \begin{cases}
\frac{-\alpha h_{ab} \bar{c}_{ab} \phi_{ab}}{\bar{\rho}_{ab}}
  & \ten{u}_{ab}\cdot \ten{r}_{ab} < 0, \\
  0 & \ten{u}_{ab}\cdot \ten{r}_{ab} \ge 0,
\end{cases}
\end{align}
where,
%
\begin{equation}
  \label{eq:av-phiij}
  \phi_{ab} = \frac{\ten{u}_{ab} \cdot \ten{r}_{ab}}{r^2_{ab} + 0.01 h^2_{ab}},
\end{equation}
%
where $\ten{r}_{ab} = \ten{r}_a - \ten{r}_b$, $\ten{u}_{ab} = \ten{u}_a -
\ten{u}_b$, $h_{ab} = (h_a + h_b)/2$, $\bar{\rho}_{ab} = (\rho_a + \rho_b)/2$,
$\bar{c}_{ab} = (c_a + c_b) / 2$, and $\alpha$ is the artificial
viscosity parameter.

The Jaumann's formulation for Hooke's stress provides us with the rate of
change of deviatoric stress,
\begin{equation}
  \label{eq:jaumann-stress-rate}
  \frac{d \sigma'_{ij}}{dt} = 2G (\dot{\epsilon}_{ij} - \frac{1}{3}
  \dot{\epsilon}_{ij} \delta_{ij}) + \sigma^{'}_{ik}  \Omega_{jk} +
  \Omega_{ik} \sigma^{'}_{kj}
\end{equation}
where $G$ is the shear modulus, $\dot{\epsilon}_{ij}$ is the strain rate tensor,
\begin{equation}
  \label{eq:strain-tensor}
  \dot{\epsilon}_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} +
  \frac{\partial u_j}{\partial x_i} \bigg)
\end{equation}
and $\Omega_{ij}$ is the rotational tensor,
\begin{equation}
  \label{eq:rotational-tensor}
  \Omega_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} -
  \frac{\partial u_j}{\partial x_i} \bigg)
\end{equation}

\begin{equation}
  \label{eq:pressure-equation}
  p = K \bigg(\frac{\rho}{\rho_{0}} - 1 \bigg),
\end{equation}
where $K = \rho_{0} c_0^2$ is the bulk modulus. Here, the constants $c_0$ and
$\rho_0$ are the reference speed of sound and density, respectively.

\subsection{Boundary conditions}

\subsection{Time integration}

@@

\subsection{Total energy of the structure}
\label{sec:total-energy-struct}

\citet{khayyer2018enhanced} had an extra section where he discusses about the
energy conservation properties of the proposed FSI scheme. He discusses
different energies in structure, kinetic energy and strain energy.

@@

The papers we have followed for the benchmarks are
\citet{sun2021accurate}, \citet{yang2016numerical}, \citet{Sun2019study},
\citet{He2017coupled}, \citet{khayyer2018enhanced}, \citet{sun2015numerical},
\citet{wang2020scale}, \citet{peng2021coupling}, \citet{zhang2021deltasph},
\citet{zhan2019stabilized}, \citet{khayyer2021multi},
\citet{long2021coupling}, \citet{ng2020coupled},

@@

This has two simulations, one taken from \cite{ng2020coupled} and \cite{khayyer2021coupled}.
\begin{table}[!ht]
  \centering
  \begin{tabular}[!ht]{ll}
    % \toprule
    Quantity & Values \\
    % \midrule
    $D$, Diameter & 2m \\
    $\rho_0$, reference density & 1000kg/m\textsuperscript{3} \\
    $c_s$ & 10m/s \\
    $D/\Delta x_{\max}$, lowest resolution & 4 \\
    $D/\Delta x_{\min} $, highest resolution & 160, 250, 500\\
    $C_r$ & 1.08 \\
    Reynolds number & 40, 550, 1000, 3000, and 9500 \\
    Time of simulation & 6 \\
    % \bottomrule
  \end{tabular}
  \caption{Parameters used for the flow past a circular cylinder problem.}%
  \label{tab:fpc-params}
\end{table}
%
%
%
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{images/hydrostatic_water_column_on_an_elastic_plate/hydrostatic_water_column_on_an_elastic_plate}
  \caption{Hydrostatic tank}
\label{fig:hs-water-on-plate}
\end{figure}
%
%

\todoin{Comment on the Poisson ratio range of the current scheme}
\todoin{Who did it previously}
\todoin{How to derive the analytical solution in short}
\todoin{Write about the different resolutions}
\todoin{Any other artificial parameters regarding the scheme, alpha, beta}

\todoin{In this problem we check the accuracy and stability-preserving property of the
proposed scheme in handling the fluid structure interaction. This problem has
been studied in Li et al. (2015), Fourey et al. (2017), Khayyer et
al. (2018a), Hu et al. (2019), (2021), (2021) papers. This benchmark has an
analytical solution derived in Li et al. (2015).}

The first benchmark test to validate the fluid structure interaction model
corresponds to an elastic plate under a hydrostatic water tank. An elastic
plate of length 1m and width of 5cm is placed under a block of water column of
height 2m is allowed to settle under gravity. The elastic plate is fixed on
both the ends. The material properties of the water are as follows, the
density is 1000 $kg/m^3$, viscosity of $1e-6$. And the material properties of
the elastic plate are as follows, density 2700$kg/m^3$, Young's modulus
$67.5 \times 10^7$ Pa and a Poisson ratio of 0.34. Three different particle
spacing are considered. Initially the fluid is set up with a hydrostatic
pressure distribution as in equation,
%
%
\begin{equation}
  f_a^F = -m_i \sum_{a} m_a \bigg(\frac{p_a}{\rho_{a}^2} +
  \frac{p_i}{\rho_{i}^2} + \Pi_{ai} \bigg) \nabla_{a} W(x_{ai}).
\end{equation}
%
%
Once the plate reaches an equilibrium state, the
deflection at the midpoint is compared with the analytical solution,
%
%
\begin{equation}
  f_a^F = -m_i \sum_{a} m_a \bigg(\frac{p_a}{\rho_{a}^2} +
  \frac{p_i}{\rho_{i}^2} + \Pi_{ai} \bigg) \nabla_{a} W(x_{ai}).
\end{equation}
%
%
%
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=1\textwidth]{figures/khayyer_2021_hydrostatic_water_column_on_composite_elastic_plate/y_amplitude}
  \caption{Hydrostatic tank}
\label{fig:y-disp-hs-water-on-plate}
\end{figure}
%
%
\Cref{fig:y-disp-hs-water-on-plate} depicts the time histories of the plate's
center point deflection with three different particle spacing. From the
presented \Cref{fig:y-disp-hs-water-on-plate} and table \todoin{citetable} we
can see as the particle spacing is reduced the numerical solution by the
current model approaches the analytical model, which proves the convergence
properties of the current scheme. \todoin{compare with other numerical schemes}
%
%
%
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=1\textwidth]{figures/khayyer_2021_hydrostatic_water_column_on_composite_elastic_plate/y_amplitude}
  \caption{Hydrostatic tank}
\label{fig:p-hs-tank-elastic-plate}
\end{figure}
%
%
%
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=1\textwidth]{figures/khayyer_2021_hydrostatic_water_column_on_composite_elastic_plate/y_amplitude}
  \caption{Hydrostatic tank}
\label{fig:sigma-hs-tank-elastic-plate}
\end{figure}

\Cref{fig:p-hs-tank-elastic-plate} shows the pressure distribution in the
fluid domain at different time histories. \Cref{fig:sigma-hs-water-on-plate}
shows the plots of $\sigma_{00}$ distribution of the elastic plate at
different time steps.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% fill-column: 78
%%% End:

>>>>

Xu has introduced the particle shifting and adjusted the particles and applied
it to fluid problems. TVF is a new variant which unifies the formulation and
applied it to fluid problems. This TVF has been generalized and applied to free
surface problems as well as elastic solid problems.

@@

continuity equation
\begin{equation}
  \label{eq:ce}
  \frac{d \rho}{d t} = - \rho \; \frac{\partial u_i}{\partial x_i},
\end{equation}
and by the momentum equation
\begin{equation}
  \label{eq:me}
  \frac{d u_i}{d t} = \frac{1}{\rho} \; \frac{\partial \sigma_{ij}}{\partial x_j}
  + g_i,
\end{equation}
with $\frac{{d} }{d t}$, $\rho$, $t$, $u_i$, $x_i$, $\sigma_{ij}$ and $g_{i}$
denoting material derivative, density, time, velocity vector, position vector,
stress tensor and gravity, respectively.

The stress tensor is split into isotropic and deviatoric parts,
\begin{equation}
  \label{eq:stress_tensor_decomposition}
  \sigma_{ij} = - p \; \delta_{ij} + \sigma'_{ij},
\end{equation}
where $p$ and $\delta_{ij}$ denote pressure and Kronecker delta function, while
$\sigma'_{ij}$ is the deviatoric stress.

The rate of change of deviatoric stress $\frac{d \sigma'_{ij}}{dt}$ can be
computed from the strain rate $\dot{\epsilon}_{ij}$ and rotation tensor
$\dot{\Omega}_{ij}$ according to Jaumann's formulation for Hooke's stress law
as
\begin{equation}
  \label{eq:jaumann-stress-rate}
  \frac{d \sigma'_{ij}}{dt} = 2G (\dot{\epsilon}_{ij} - \frac{1}{3}
  \dot{\epsilon}_{kk} \delta_{ij}) + \sigma^{'}_{ik}  \Omega_{jk} +
  \Omega_{ik} \sigma^{'}_{kj}.
\end{equation}
Here $G$ is the shear modulus, while $\dot{\epsilon}_{ij}$ is
\begin{equation}
  \label{eq:strain-tensor}
  \dot{\epsilon}_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} +
  \frac{\partial u_j}{\partial x_i} \bigg),
\end{equation}
and $\Omega_{ij}$ is
\begin{equation}
  \label{eq:rotational-tensor}
  \Omega_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} -
  \frac{\partial u_j}{\partial x_i} \bigg).
\end{equation}

For a weakly-compressible or incompressible fluid the deviatoric stress
vanishes and a viscous force is added to the stress tensor:
\begin{equation}
  \label{eq:fluid-stress-decomposition}
  \sigma_{ij} = - p \delta_{ij} + 2 \eta \frac{\partial u_i}{\partial x_j}
\end{equation}
where $\eta$ is the kinematic viscosity of the fluid.

In both fluid and solid modelling the pressure is computed using an
isothermal equation of state, given as,
\begin{equation}
  \label{eq:pressure-equation}
  p = K \bigg(\frac{\rho}{\rho_{0}} - 1 \bigg),
\end{equation}
where $K = \rho_{0} c_0^2$ is the bulk modulus. Here, the constants $c_0$ and
$\rho_0$ are the reference speed of sound and density, respectively. For solids,
$c_0$ is computed as $\sqrt{\frac{E}{3 (1 - 2 \nu)\rho_{0}}}$, $\nu$ is the
Poisson ratio.

\section{Numerical method}

Write about Material derivative

\begin{equation}
  \label{eq:modified-material-derivative}
  \frac{\tilde{d} }{d t} = \frac{\partial }{\partial t} +
  \tilde{u}_j \frac{\partial }{\partial x_j}.
\end{equation}

\begin{equation}
  \label{eq:ce-tvf}
  \frac{\tilde{d} \rho}{d t} =
  - \rho \frac{\partial \tilde{u}_j}{\partial x_j} +
  \frac{\partial (\rho (\tilde{u}_j - u_j))}{\partial x_j}.
\end{equation}

\begin{equation}
  \label{eq:mom-tvf}
  \frac{\tilde{d} u_i}{d t} =
  \frac{\partial}{\partial x_j} (u_i (\tilde{u}_j - u_j))
  - u_i \frac{\partial}{\partial x_j} (\tilde{u}_j - u_j)
  + g_i
  +\frac{1}{\rho} \frac{\partial \sigma_{ij}}{\partial x_j}.
\end{equation}

\begin{equation}
  \label{eq:edac-p-evolve}
  \frac{\tilde{d} p}{d t} =
  (p -\rho c_s^2)
    \text{div}(\ten{u})
  - p \; \text{div}(\tilde{\ten{u}})
    + \text{div}(p (\tilde{\ten{u}} - \ten{u}))
    + \nu_{edac}  \nabla^2 p.
\end{equation}
%
The value of $\nu_{edac}$ is,
\begin{equation}
  \label{eq:nu-edac}
  \nu_{edac} = \frac{\alpha_{\textrm{edac}} h c_s}{8},
\end{equation}

\subsection{SPH discretization}

In the current work, both fluid and solid modelling uses the same continuity
and pressure evolution equation. The SPH discretization of the continuity
equation~\eqref{eq:ce-tvf} and the pressure evolution
equation~\eqref{eq:edac-p-evolve} respectively are,
\begin{equation}
  \label{eq:sph-discretization-continuity}
  \frac{\tilde{d}\rho_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; (
  \rho_{a} \; \tilde{\ten{u}}_{ab} \; + \;
  (\rho \; (\tilde{\ten{u}} \; - \;
  \ten{u}))_{ab}) \; \cdot \nabla_{a} W_{ab},
\end{equation}

\begin{multline}
  \label{eq:sph-discretization-edac}
  \frac{\tilde{d}p_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; \bigg(
  (p_{a} - \rho_{a} c_{s}^2) \; \ten{u}_{ab} \; + \;
  p_{a} \; \tilde{\ten{u}}_{ab} \; - \;
  (p \; (\tilde{\ten{u}} - \ten{u}))_{ab} \; + \; \\
  4 \; \nu_{edac}
  \frac{p_a - p_b}{(\rho_a + \rho_b) (r^2_{ab} + 0.01 h_{ab}^{2})} \ten{r}_{ab}
  \bigg) \; \cdot \nabla_{a} W_{ab}.
\end{multline}
%
Similarly, the discretized momentum equation for fluids is written as,
\begin{multline}
  \label{eq:sph-momentum-fluid}
  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2} + \Pi_{ab}
  \ten{I} \bigg) \bigg]
  \cdot \nabla_{a} W_{ab} \\
  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
  \nabla_{a} W_{ab} + \sum_{b} m_b \frac{4 \eta \nabla W_{ab}\cdot
    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab} +
  \ten{g}_{a},
\end{multline}
where $\ten{A}_a = \rho_a \ten{u}_a \otimes (\ten{\tilde{u}}_a - \ten{u}_a)$,
$\ten{I}$ is the identity matrix, $\eta$ is the kinematic viscosity of the
fluid and \citet{morris1997modeling} formulation is used to discretize the
viscosity term. $\Pi_{ab}$ is the artificial
viscosity~\cite{monaghan-review:2005} to maintain the stability of the
numerical scheme. It is given as,
\begin{align}
  \label{eq:mom-av}
  \Pi_{ab} =
  \begin{cases}
\frac{-\alpha h_{ab} \bar{c}_{ab} \phi_{ab}}{\bar{\rho}_{ab}}
  & \ten{u}_{ab}\cdot \ten{r}_{ab} < 0, \\
  0 & \ten{u}_{ab}\cdot \ten{r}_{ab} \ge 0,
\end{cases}
\end{align}
where,
%
\begin{equation}
  \label{eq:av-phiij}
  \phi_{ab} = \frac{\ten{u}_{ab} \cdot \ten{r}_{ab}}{r^2_{ab} + 0.01 h^2_{ab}},
\end{equation}
%
where $\ten{r}_{ab} = \ten{r}_a - \ten{r}_b$, $\ten{u}_{ab} = \ten{u}_a -
\ten{u}_b$, $h_{ab} = (h_a + h_b)/2$, $\bar{\rho}_{ab} = (\rho_a + \rho_b)/2$,
$\bar{c}_{ab} = (c_a + c_b) / 2$, and $\alpha$ is the artificial
viscosity parameter.

%
For solid mechanics the momentum equation is written as,
\begin{equation}
  \label{eq:sph-momentum-solid}
  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\teng{\sigma}^{'}_{a}}{\rho_a^2} +
  \frac{\teng{\sigma}^{'}_{b}}{\rho_b^2} + \Pi_{ab} \ten{I} \bigg) \bigg]  \cdot \nabla_{a} W_{ab} +
  \ten{g}_{a},
\end{equation}
we have not considered the correction stress term $\ten{A}$ in momentum
equation of solid mechanics as it has a negligible effect.

In addition to these three equations, the Jaumann stress rate equation is also
solved. In the current work we use the momentum velocity $\ten{u}$ rather than
$\tilde{\ten{u}}$ as in the GTVF~\cite{zhang_hu_adams17} in the computation of
gradient of velocity. The SPH discretization of the gradient of velocity is
given as,
\begin{equation}
  \label{eq:sph-vel-grad}
  \nabla \ten{u}_a =
  - \sum_{b} \frac{m_b}{\rho_{b}} (\ten{u}_{a} - \ten{u}_{b}) \otimes (\nabla_{a} W_{ab}),
\end{equation}
where $\otimes$ is the outer product.

The SPH discretization of the modified Jaumann stress rate
\cref{eq:modified-jaumann-stress-rate} is given as,
\begin{multline}
  \label{eq:sph-modified-jaumann-stress}
  \frac{\tilde{d}\teng{\sigma}^{'}_{a}}{dt} = 2G (\dot{\teng{\epsilon}}_{a} -
  \frac{1}{3} \dot{\teng{\epsilon}}_{a} \ten{I}) + \teng{\sigma}^{'}_{a}
  \teng{\Omega}_{a}^{T} +
  \teng{\Omega}_{a} \teng{\sigma}^{'}_{a} + \\
  + \sum_{b} \; \frac{m_b}{\rho_{b}} \; (\teng{\sigma}^{'} \otimes (\tilde{\ten{u}} -
  \ten{u}))_{ab} \; \cdot \nabla_{a} W_{ab}
  + \teng{\sigma}^{'}_{a} \sum_{b} \; \frac{m_b}{\rho_{b}} \;
  (\tilde{\ten{u}} - \ten{u})_{ab} \; \cdot \nabla_{a} W_{ab}.
\end{multline}

\subsection{Transport velocity computation of the mediums}

The particles in the current scheme are moved with the transport velocity,
\begin{equation}
  \label{eq:transport_velocity_position_derivative}
  \frac{d\ten{r}_a}{dt} = \ten{\tilde{u}}_a.
\end{equation}
%
The transport velocity is updated using,
\begin{equation}
  \label{eq:transport_velocity}
  \ten{\tilde{u}}_a(t + \Delta t) =\ten{u}_a(t) + \Delta t \; \frac{\tilde{d} \ten{u}_a}{dt} +
  \bigg(\frac{d \ten{u}_{a}}{dt}\bigg)_{\text{c}} \Delta t
\end{equation}

Where $\big(\frac{d \ten{u}_a}{dt}\big)_{\text{c}}$ is the homogenization
acceleration which ensures that the particle positions are homogeneous. In the
current work we have explored two kinds of homogenization accelerations, one
is a displacement based technique due to \citet{sun2017deltaplus}, and the
other is the iterative particle shifting technique due to
\citet{huang_kernel_2019}. These are discussed in the following.

\subsubsection{Transport velocity computation of fluid medium}
\label{sec:fluid_pst}

In \citet{sun2017deltaplus}, the particle shifting technique was implemented as
a particle displacement ($\delta \ten{r}$). This was modified in
\citet{sun_consistent_2019} to be computed as a change to the velocity. In the
present work we modify this to be treated as an acceleration to the particle
in order to unify the treatment of different PST methods.

Firstly, the velocity deviation based equation is given as,
\begin{equation}
  \label{eq:sun2019_pst}
  \delta \ten{u}_a = - \text{Ma} \; (2h) c_0 \sum_b \bigg[
  1 + R \bigg( \frac{W_{ab}}{W(\Delta x)} \bigg)^n  \bigg] \nabla_a W_{ab} V_b,
\end{equation}
%
it is modified to force based as,
\begin{equation}
  \label{eq:sun2019_pst}
  \bigg(\frac{d \ten{u}_a}{dt}\bigg)_{\text{c}} = - \frac{\text{Ma} \;
    (2h) c_0}{\Delta t} \sum_b \bigg[1 + R \bigg( \frac{W_{ab}}{W(\Delta x)} \bigg)^n
  \bigg] \nabla_a W_{ab} V_b,
\end{equation}
where $R$ is an adjustment factor to handle the tensile instability, and
$\text{Ma}$ is the mach number of the flow. $V_b$ is the volume of the
$b$\textsuperscript{th} particle. The acceleration is changed to account for
particles that are on the free surface. We use $R = 0.2$ and $n = 4$ as
suggested by \citet{sun_consistent_2019}.

\subsubsection{Transport velocity computation of solid medium}
\label{sec:elastic_solid_pst}

In \citet{sun2017deltaplus}, the particle shifting technique was implemented as
a particle displacement ($\delta \ten{r}$). This was modified in
\citet{sun_consistent_2019} to be computed as a change to the velocity. In the
present work we modify this to be treated as an acceleration to the particle
in order to unify the treatment of different PST methods.

Firstly, the velocity deviation based equation is given as,
\begin{equation}
  \label{eq:sun2019_pst}
  \delta \ten{u}_a = - \text{Ma} \; (2h) c_0 \sum_b \bigg[
  1 + R \bigg( \frac{W_{ab}}{W(\Delta x)} \bigg)^n  \bigg] \nabla_a W_{ab} V_b,
\end{equation}
%
it is modified to force based as,
\begin{equation}
  \label{eq:sun2019_pst}
  \bigg(\frac{d \ten{u}_a}{dt}\bigg)_{\text{c}} = - \frac{\text{Ma} \;
    (2h) c_0}{\Delta t} \sum_b \bigg[1 + R \bigg( \frac{W_{ab}}{W(\Delta x)} \bigg)^n
  \bigg] \nabla_a W_{ab} V_b,
\end{equation}
where $R$ is an adjustment factor to handle the tensile instability, and
$\text{Ma}$ is the mach number of the flow. $V_b$ is the volume of the
$b$\textsuperscript{th} particle. The acceleration is changed to account for
particles that are on the free surface. We use $R = 0.2$ and $n = 4$ as
suggested by \citet{sun_consistent_2019}.

\section{Fluid structure interaction}

@@

% \subsection{Total energy of the structure}
% \label{sec:total-energy-struct}

% \citet{khayyer2018enhanced} had an extra section where he discusses about the
% energy conservation properties of the proposed FSI scheme. He discusses
% different energies in structure, kinetic energy and strain energy.

\section{Summary equations of the full model to be solved}

\subsection{Summary equations fluid model}

\begin{multline}
  \label{eq:sph-discretization-edac}
  \frac{\tilde{d}p_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; \bigg(
  (p_{a} - \rho_{a} c_{s}^2) \; \ten{u}_{ab} \; + \;
  p_{a} \; \tilde{\ten{u}}_{ab} \; - \;
  (p \; (\tilde{\ten{u}} - \ten{u}))_{ab} \; + \; \\
  4 \; \nu_{edac}
  \frac{p_a - p_b}{(\rho_a + \rho_b) (r^2_{ab} + 0.01 h_{ab}^{2})} \ten{r}_{ab}
  \bigg) \; \cdot \nabla_{a} W_{ab}.
\end{multline}
%

\begin{multline}
  \label{eq:sph-momentum-fluid}
  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2} + \Pi_{ab}
  \ten{I} \bigg) \bigg]
  \cdot \nabla_{a} W_{ab} \\
  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
  \nabla_{a} W_{ab} + \sum_{b} m_b \frac{4 \eta \nabla W_{ab}\cdot
    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab} +
  \ten{g}_{a},
\end{multline}

\begin{equation}
  \label{eq:transport_velocity}
  \ten{\tilde{u}}_a(t + \Delta t) =\ten{u}_a(t) + \Delta t \; \frac{\tilde{d} \ten{u}_a}{dt} +
  \bigg(\frac{d \ten{u}_{a}}{dt}\bigg)_{\text{c}} \Delta t
\end{equation}

\begin{equation}
  \label{eq:gtvf_pst}
  \bigg(\frac{d \ten{u}_a}{dt}\bigg)_{\text{c}} = p_a^0 \;
  \sum_b m_b \frac{1}{\rho_a^2} \nabla_a \widetilde{W}_{ab} ,
\end{equation}

\subsection{Summary equations solid model}

\begin{equation}
  \label{eq:sph-modified-jaumann-stress}
  \frac{\tilde{d}\teng{\sigma}^{'}_{a}}{dt} = 2G (\dot{\teng{\epsilon}}_{a} -
  \frac{1}{3} \dot{\teng{\epsilon}}_{a} \ten{I}) + \teng{\sigma}^{'}_{a}
  \teng{\Omega}_{a}^{T} +
  \teng{\Omega}_{a} \teng{\sigma}^{'}_{a}
\end{equation}

\begin{equation}
  \label{eq:strain-tensor}
  \dot{\epsilon}_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} +
  \frac{\partial u_j}{\partial x_i} \bigg),
\end{equation}
and $\Omega_{ij}$ is the rotation tensor,
\begin{equation}
  \label{eq:rotational-tensor}
  \Omega_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} -
  \frac{\partial u_j}{\partial x_i} \bigg).
\end{equation}

\begin{equation}
  \label{eq:transport_velocity}
  \ten{\tilde{u}}_a(t + \Delta t) =\ten{u}_a(t) + \Delta t \; \frac{\tilde{d} \ten{u}_a}{dt} +
  \bigg(\frac{d \ten{u}_{a}}{dt}\bigg)_{\text{c}} \Delta t
\end{equation}

\begin{equation}
  \label{eq:sun2019_pst}
  \bigg(\frac{d \ten{u}_a}{dt}\bigg)_{\text{c}} = - \frac{\text{Ma} \;
    (2h) c_0}{\Delta t} \sum_b \bigg[1 + R \bigg( \frac{W_{ab}}{W(\Delta x)} \bigg)^n
  \bigg] \nabla_a W_{ab} V_b,
\end{equation}

@@

@@

In the first example, a hydrostatic water column on an elastic plate is
considered. The initial setup of the system with water pressure is shown in
figure, where an initial column of fluid under hydrostatic state is rested on an
elastic plate under gravity. The water column is $2$ m in height and $0.5$ m in
width, while the elastic plate is of $0.05$ m in thickness and $0.5$ m in
length, respectively. The elastic plate considered here is made of Aluminium,
whose material properties are: Young's modulus $E = 67.5$ GPa, Poisson's ratio
$\nu = 0.4$. According to the analytical solution \cite{sfsfd}, the deflection
magnitude at mid-span after the system's equilibrium state is
$d = -6.85 \times 10^{-5}$ m.

%
%
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/good_vs_bad}
  \caption{Hydrostatic water column on an elastic plate}
\label{fig:hs-water-on-plate}
\end{figure}
%
%

The simulation is ran for a total time of 0.4 s. For convergence study, three
different particle resolutions, respectively
$h_e / delta_x = 10, h_e / delta_x = 10, h_e / delta_x = 10 $are adopted,
whose respective total number of particles are 1122232 and 1122323. The time
step of the fluid and solid phase are computed separately, but we use
substepping to update the fluid and solid phases as per section
\ref{section:substepping}.

%
%
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/good_vs_bad}
  \caption{Hydrostatic water column on an elastic plate}
\label{fig:hs-water-on-plate}
\end{figure}
%
%

% This has two simulations, one taken from \cite{ng2020coupled} and \cite{khayyer2021coupled}.
% \begin{table}[!ht]
%   \centering
%   \begin{tabular}[!ht]{ll}
%     % \toprule
%     Quantity & Values \\
%     % \midrule
%     $D$, Diameter & 2m \\
%     $\rho_0$, reference density & 1000kg/m\textsuperscript{3} \\
%     $c_s$ & 10m/s \\
%     $D/\Delta x_{\max}$, lowest resolution & 4 \\
%     $D/\Delta x_{\min} $, highest resolution & 160, 250, 500\\
%     $C_r$ & 1.08 \\
%     Reynolds number & 40, 550, 1000, 3000, and 9500 \\
%     Time of simulation & 6 \\
%     % \bottomrule
%   \end{tabular}
%   \caption{Parameters used for the flow past a circular cylinder problem.}%
%   \label{tab:fpc-params}
% \end{table}
% %
%

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
